---
output:
  word_document:
    toc: yes
    reference_docx: template1.docx
toc-title: 'Vocabulary paper results: Weighted photactic probability + Frequency (v3)'

---

<!-- loading packages, user-defined functions and datasets -->
```{r echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE, include=FALSE}
lib <- c("ggplot2", "dplyr","stringr","knitr","gridExtra",
         "lme4","car","kableExtra", "magick", "grid")
lapply(lib, require, character.only = TRUE)
load(file="ws4.RData")

options(knitr.table.format = 'markdown')
```

<!-- set folder for graphs -->
```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  fig.path = "images/"
)
```

<!-- additional funs -->
```{r echo = FALSE}
grid_arrange_shared_legend <- function(..., nrow = 1,y_title, x_size, y_size,widths1 = 2, widths2=0.2,hjust1=1, x_title, ncol = length(list(...)), position = c("bottom", "right")) {

  plots <- list(...)
  position <- match.arg(position)
  g <- ggplotGrob(plots[[1]] + theme(legend.position = position))$grobs
  legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
  lheight <- sum(legend$height)
  lwidth <- sum(legend$width)
  gl <- lapply(plots, function(x) x + theme(legend.position = "none"))
  gl <- c(gl, nrow = nrow, ncol = ncol)

  combined <- switch(position,
                     "bottom" = arrangeGrob(do.call(arrangeGrob, gl),
                                            legend,
                                            ncol = 1,
                                            heights = unit.c(unit(1, "npc") - lheight, lheight)),
                     "right" = arrangeGrob(do.call(arrangeGrob, gl),
                                           legend,
                                           ncol = 2,
                                           widths = c(widths1, widths2),
                                           left=textGrob(y_title, gp=gpar(fontsize=y_size), rot = 90),
                                           bottom=textGrob(x_title, gp=gpar(fontsize=x_size), vjust = 0, hjust = hjust1)))
  grid.newpage()
  grid.draw(combined)

}

```

### Phonotactic probability

<br>

IPhOD Weighted phonotactic probability measure based on written log (base 10) word frequencies from the [SUBTLEXus database](https://www.ugent.be/pp/experimentele-psychologie/en/research/documents/subtlexus) (Brysbaert & New, 2009). 

<br>

#### Quantiles table

```{r echo = FALSE, message=FALSE, warning=FALSE}
  subtlex_us_pp %>%
    filter(Input %in% (mot_uni_on_subtlex_us$phon %>% 
                         unlist() %>%
                         str_replace_all("_", ".") %>%
                         str_replace_all("UU", "AH") %>%
                         c(chi_uni_on_subtlex_us$phon %>% 
                             unlist() %>%
                             str_replace_all("_", ".") %>%
                             str_replace_all("UU", "AH"))
    )) %>%
    .$unsLBPAV %>%
    quantile(na.rm = TRUE) %>%
  as.matrix() %>%
  t() %>%
  kable()
```

<br>

```{r logpp_main, echo = FALSE, results='asis', fig.width=16, fig.height=9}
plot_pp <- function(df, main_title) {
  ggplot(df, aes(x=section, y=ph_pr_qu1_perc, fill=baby, shape="Q1")) + 
  geom_point(size=4, alpha=0.2) +
  scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
  labs(x = " ", y = " ") +
  ggtitle(main_title) +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) +
  geom_point(aes(x=section, y=ph_pr_qu2_perc, fill=baby, shape="Q2"),size=4, alpha=0.2) + 
  geom_point(aes(x=section, y=ph_pr_qu3_perc, fill=baby, shape="Q3"), size=4,alpha=0.2) + 
  geom_point(aes(x=section, y=ph_pr_qu4_perc, fill=baby, shape="Q4"), size=4,alpha=0.2) + 
  scale_shape_manual("PP Quartile", values=c(`Q1`= 0, `Q2`= 3, `Q3` = 2, `Q4`=1),
                     breaks=c("Q1","Q2", "Q3","Q4"))+
  scale_y_continuous(limits=c(0, 70), breaks=seq(0, 70, by = 10))+
  guides(fill=FALSE)+
  geom_smooth(aes(x=section, y=ph_pr_qu1_perc,linetype="Q1"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=ph_pr_qu2_perc,linetype="Q2"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=ph_pr_qu3_perc,linetype="Q3"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=ph_pr_qu4_perc,linetype="Q4"), fill=NA, colour="black", method="lm", size=0.8)+
  theme(axis.text=element_text(size=18),         legend.text = element_text(size = 20),         legend.title = element_text(size = 20),         legend.key.size = unit(1, "cm"))+     scale_colour_grey(start = 0, end = .9)+
  scale_linetype_manual("PP Quartile", values=c(`Q4` = "dotdash", `Q1` = "longdash",`Q2` = "solid", `Q3`= "dotted"), breaks=c("Q1","Q2", "Q3","Q4"))
}

plot1 <- plot_pp(chi_uni_on_subtlex_us, "Children") 
plot2 <- plot_pp(mod_on_subtlex_us, "Model") 
plot3 <- plot_pp(mot_uni_on_subtlex_us, "Mothers") 

grid_arrange_shared_legend(plot3, plot1, plot2, position = "right", 
                           x_title = "Stage", y_title = "Novel words (%)",
                           x_size = 25, y_size = 25,
                           widths1 = 2, widths2 = 0.5, hjust1 = 1)
```

**Figure.** Breakdown of PP by quartile

<br>

### Phonotactic probability at each phonemic word length

<br>

```{r logpp_length1, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(log_pp_lengths[["chi_uni_len2"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len2"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len2"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len2"]]$ph_pr_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(log_pp_lengths[["chi_uni_len3"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len3"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len3"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len3"]]$ph_pr_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(log_pp_lengths[["chi_uni_len4"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len4"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len4"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len4"]]$ph_pr_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len5 <- c(sum(log_pp_lengths[["chi_uni_len5"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len5"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len5"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len5"]]$ph_pr_qu4))
table_chi_len5 <- table_chi_len5/sum(table_chi_len5)*100
table_chi_len6 <- c(sum(log_pp_lengths[["chi_uni_len6"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len6"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len6"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len6"]]$ph_pr_qu4))
table_chi_len6 <- table_chi_len6/sum(table_chi_len6)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2,table_chi_len3,table_chi_len4,table_chi_len5,table_chi_len6), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD breakdown with quartiles computed for 2-6 phonemes across all mother and child words, using the same quartiles to breakdown each length

<br>

```{r logpp_length2, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(log_pp_lengths[["mod_len2"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len2"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len2"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len2"]]$ph_pr_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(log_pp_lengths[["mod_len3"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len3"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len3"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len3"]]$ph_pr_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(log_pp_lengths[["mod_len4"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len4"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len4"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len4"]]$ph_pr_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len5 <- c(sum(log_pp_lengths[["mod_len5"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len5"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len5"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len5"]]$ph_pr_qu4))
table_chi_len5 <- table_chi_len5/sum(table_chi_len5)*100
table_chi_len6 <- c(sum(log_pp_lengths[["mod_len6"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len6"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len6"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len6"]]$ph_pr_qu4))
table_chi_len6 <- table_chi_len6/sum(table_chi_len6)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2,table_chi_len3,table_chi_len4,table_chi_len5,table_chi_len6), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** MODEL breakdown with quartiles computed for 2-6 phonemes across all mother and child words, using the same quartiles to breakdown each length

<br>

```{r logpp_length3, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2b <- c(sum(log_pp_lengths[["chi_uni_len2b"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len2b"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len2b"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len2b"]]$ph_pr_qu4))
table_chi_len2b <- table_chi_len2b/sum(table_chi_len2b)*100

table_chi_len3b <- c(sum(log_pp_lengths[["chi_uni_len3b"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len3b"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len3b"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len3b"]]$ph_pr_qu4))
table_chi_len3b <- table_chi_len3b/sum(table_chi_len3b)*100
table_chi_len4b <- c(sum(log_pp_lengths[["chi_uni_len4b"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len4b"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len4b"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len4b"]]$ph_pr_qu4))
table_chi_len4b <- table_chi_len4b/sum(table_chi_len4b)*100
table_chi_len5b <- c(sum(log_pp_lengths[["chi_uni_len5b"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len5b"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len5b"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len5b"]]$ph_pr_qu4))
table_chi_len5b <- table_chi_len5b/sum(table_chi_len5b)*100
table_chi_len6b <- c(sum(log_pp_lengths[["chi_uni_len6b"]]$ph_pr_qu1), sum(log_pp_lengths[["chi_uni_len6b"]]$ph_pr_qu2),sum(log_pp_lengths[["chi_uni_len6b"]]$ph_pr_qu3),sum(log_pp_lengths[["chi_uni_len6b"]]$ph_pr_qu4))
table_chi_len6b <- table_chi_len6b/sum(table_chi_len6b)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2b,table_chi_len3b,table_chi_len4b,table_chi_len5b,table_chi_len6b), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
    theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD breakdown with quartiles computed for 2-6 phonemes across all mother and child words, this time computing quartiles individually for each phonemic length

<br>

```{r logpp_length4, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2b <- c(sum(log_pp_lengths[["mod_len2b"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len2b"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len2b"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len2b"]]$ph_pr_qu4))
table_chi_len2b <- table_chi_len2b/sum(table_chi_len2b)*100
table_chi_len3b <- c(sum(log_pp_lengths[["mod_len3b"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len3b"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len3b"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len3b"]]$ph_pr_qu4))
table_chi_len3b <- table_chi_len3b/sum(table_chi_len3b)*100
table_chi_len4b <- c(sum(log_pp_lengths[["mod_len4b"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len4b"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len4b"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len4b"]]$ph_pr_qu4))
table_chi_len4b <- table_chi_len4b/sum(table_chi_len4b)*100
table_chi_len5b <- c(sum(log_pp_lengths[["mod_len5b"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len5b"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len5b"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len5b"]]$ph_pr_qu4))
table_chi_len5b <- table_chi_len5b/sum(table_chi_len5b)*100
table_chi_len6b <- c(sum(log_pp_lengths[["mod_len6b"]]$ph_pr_qu1), sum(log_pp_lengths[["mod_len6b"]]$ph_pr_qu2),sum(log_pp_lengths[["mod_len6b"]]$ph_pr_qu3),sum(log_pp_lengths[["mod_len6b"]]$ph_pr_qu4))
table_chi_len6b <- table_chi_len6b/sum(table_chi_len6b)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2b,table_chi_len3b,table_chi_len4b,table_chi_len5b,table_chi_len6b), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
    theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** MODEL breakdown with quartiles computed for 2-6 phonemes across all mother and child words, this time computing quartiles individually for each phonemic length

<br> 

### General Frequency
IPhOD General Frequency measure based on [SUBTLEXus](https://www.ugent.be/pp/experimentele-psychologie/en/research/documents/subtlexus) (Brysbaert & New, 2009). 
Words that are not present in IPhOD have no frequency value and therefore were excluded.

<br>

#### Quantiles table

```{r echo = FALSE, message=FALSE, warning=FALSE}
  iphod_freq %>%
    filter(UnTrn %in% (mot_uni_on_freq$phon %>% 
                         unlist() %>%
                         str_replace_all("_", ".") %>%
                         str_replace_all("UU", "AH") %>%
                         c(chi_uni_on_freq$phon %>% 
                             unlist() %>%
                             str_replace_all("_", ".") %>%
                             str_replace_all("UU", "AH"))
    )) %>%
    .$SFreq %>%
    quantile(na.rm = TRUE) %>%
  as.matrix() %>%
  t() %>%
  kable()
```

<br>

```{r freq_main, echo = FALSE, results='asis', fig.width=16, fig.height=9}
plot_freq <- function(df, main_title) {
  ggplot(df, aes(x=section, y=freq_qu1_perc, fill=baby, shape="Q1")) + 
  geom_point(size=4, alpha=0.2) +
  scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
  labs(x = " ", y = " ") +
  ggtitle(main_title) +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) +
  geom_point(aes(x=section, y=freq_qu2_perc, fill=baby, shape="Q2"),size=4, alpha=0.2) + 
  geom_point(aes(x=section, y=freq_qu3_perc, fill=baby, shape="Q3"), size=4,alpha=0.2) + 
  geom_point(aes(x=section, y=freq_qu4_perc, fill=baby, shape="Q4"), size=4,alpha=0.2) + 
  scale_shape_manual("IPhOD Quartile", values=c(`Q1`= 0, `Q2`= 3, `Q3` = 2, `Q4`=1),
                     breaks=c("Q4","Q3", "Q2","Q1"))+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  guides(fill=FALSE)+
  geom_smooth(aes(x=section, y=freq_qu1_perc,linetype="Q1"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=freq_qu2_perc,linetype="Q2"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=freq_qu3_perc,linetype="Q3"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=freq_qu4_perc,linetype="Q4"), fill=NA, colour="black", method="lm", size=0.8)+
  theme(axis.text=element_text(size=18),         legend.text = element_text(size = 20),         legend.title = element_text(size = 20),         legend.key.size = unit(1, "cm"))+     scale_colour_grey(start = 0, end = .9)+
  scale_linetype_manual("IPhOD Quartile", values=c(`Q4` = "dotdash", `Q1` = "longdash",`Q2` = "solid", `Q3`= "dotted"), breaks=c("Q4","Q3", "Q2","Q1"))
}

plot1 <- plot_freq(chi_uni_on_freq, "Children") 
plot2 <- plot_freq(mod_on_freq, "Model") 
plot3 <- plot_freq(mot_uni_on_freq, "Mothers") 

grid_arrange_shared_legend(plot3, plot1, plot2, position = "right", 
                           x_title = "Stage", y_title = "Novel words (%)",
                           x_size = 25, y_size = 25,
                           widths1 = 2, widths2 = 0.5, hjust1 = 1)
```

**Figure.** Breakdown of General frequency by quartile

<br>

### General Frequency at each phonemic word length

<br>

```{r freq_length1, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(freq_lengths[["chi_uni_len2"]]$freq_qu1), sum(freq_lengths[["chi_uni_len2"]]$freq_qu2),sum(freq_lengths[["chi_uni_len2"]]$freq_qu3),sum(freq_lengths[["chi_uni_len2"]]$freq_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(freq_lengths[["chi_uni_len3"]]$freq_qu1), sum(freq_lengths[["chi_uni_len3"]]$freq_qu2),sum(freq_lengths[["chi_uni_len3"]]$freq_qu3),sum(freq_lengths[["chi_uni_len3"]]$freq_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(freq_lengths[["chi_uni_len4"]]$freq_qu1), sum(freq_lengths[["chi_uni_len4"]]$freq_qu2),sum(freq_lengths[["chi_uni_len4"]]$freq_qu3),sum(freq_lengths[["chi_uni_len4"]]$freq_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len5 <- c(sum(freq_lengths[["chi_uni_len5"]]$freq_qu1), sum(freq_lengths[["chi_uni_len5"]]$freq_qu2),sum(freq_lengths[["chi_uni_len5"]]$freq_qu3),sum(freq_lengths[["chi_uni_len5"]]$freq_qu4))
table_chi_len5 <- table_chi_len5/sum(table_chi_len5)*100
table_chi_len6 <- c(sum(freq_lengths[["chi_uni_len6"]]$freq_qu1), sum(freq_lengths[["chi_uni_len6"]]$freq_qu2),sum(freq_lengths[["chi_uni_len6"]]$freq_qu3),sum(freq_lengths[["chi_uni_len6"]]$freq_qu4))
table_chi_len6 <- table_chi_len6/sum(table_chi_len6)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `IPhOD quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2,table_chi_len3,table_chi_len4,table_chi_len5,table_chi_len6), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`IPhOD quartile` <- as.factor(table$`IPhOD quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `IPhOD quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD breakdown with quartiles computed for 2-6 phonemes across all mother and child words, using the same quartiles to breakdown each length

<br>

```{r freq_length2, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(freq_lengths[["mod_len2"]]$freq_qu1), sum(freq_lengths[["mod_len2"]]$freq_qu2),sum(freq_lengths[["mod_len2"]]$freq_qu3),sum(freq_lengths[["mod_len2"]]$freq_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(freq_lengths[["mod_len3"]]$freq_qu1), sum(freq_lengths[["mod_len3"]]$freq_qu2),sum(freq_lengths[["mod_len3"]]$freq_qu3),sum(freq_lengths[["mod_len3"]]$freq_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(freq_lengths[["mod_len4"]]$freq_qu1), sum(freq_lengths[["mod_len4"]]$freq_qu2),sum(freq_lengths[["mod_len4"]]$freq_qu3),sum(freq_lengths[["mod_len4"]]$freq_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len5 <- c(sum(freq_lengths[["mod_len5"]]$freq_qu1), sum(freq_lengths[["mod_len5"]]$freq_qu2),sum(freq_lengths[["mod_len5"]]$freq_qu3),sum(freq_lengths[["mod_len5"]]$freq_qu4))
table_chi_len5 <- table_chi_len5/sum(table_chi_len5)*100
table_chi_len6 <- c(sum(freq_lengths[["mod_len6"]]$freq_qu1), sum(freq_lengths[["mod_len6"]]$freq_qu2),sum(freq_lengths[["mod_len6"]]$freq_qu3),sum(freq_lengths[["mod_len6"]]$freq_qu4))
table_chi_len6 <- table_chi_len6/sum(table_chi_len6)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `IPhOD quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2,table_chi_len3,table_chi_len4,table_chi_len5,table_chi_len6), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`IPhOD quartile` <- as.factor(table$`IPhOD quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `IPhOD quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** MODEL breakdown with quartiles computed for 2-6 phonemes across all mother and child words, using the same quartiles to breakdown each length

<br>

```{r freq_length3, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2b <- c(sum(freq_lengths[["chi_uni_len2b"]]$freq_qu1), sum(freq_lengths[["chi_uni_len2b"]]$freq_qu2),sum(freq_lengths[["chi_uni_len2b"]]$freq_qu3),sum(freq_lengths[["chi_uni_len2b"]]$freq_qu4))
table_chi_len2b <- table_chi_len2b/sum(table_chi_len2b)*100

table_chi_len3b <- c(sum(freq_lengths[["chi_uni_len3b"]]$freq_qu1), sum(freq_lengths[["chi_uni_len3b"]]$freq_qu2),sum(freq_lengths[["chi_uni_len3b"]]$freq_qu3),sum(freq_lengths[["chi_uni_len3b"]]$freq_qu4))
table_chi_len3b <- table_chi_len3b/sum(table_chi_len3b)*100
table_chi_len4b <- c(sum(freq_lengths[["chi_uni_len4b"]]$freq_qu1), sum(freq_lengths[["chi_uni_len4b"]]$freq_qu2),sum(freq_lengths[["chi_uni_len4b"]]$freq_qu3),sum(freq_lengths[["chi_uni_len4b"]]$freq_qu4))
table_chi_len4b <- table_chi_len4b/sum(table_chi_len4b)*100
table_chi_len5b <- c(sum(freq_lengths[["chi_uni_len5b"]]$freq_qu1), sum(freq_lengths[["chi_uni_len5b"]]$freq_qu2),sum(freq_lengths[["chi_uni_len5b"]]$freq_qu3),sum(freq_lengths[["chi_uni_len5b"]]$freq_qu4))
table_chi_len5b <- table_chi_len5b/sum(table_chi_len5b)*100
table_chi_len6b <- c(sum(freq_lengths[["chi_uni_len6b"]]$freq_qu1), sum(freq_lengths[["chi_uni_len6b"]]$freq_qu2),sum(freq_lengths[["chi_uni_len6b"]]$freq_qu3),sum(freq_lengths[["chi_uni_len6b"]]$freq_qu4))
table_chi_len6b <- table_chi_len6b/sum(table_chi_len6b)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `IPhOD quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2b,table_chi_len3b,table_chi_len4b,table_chi_len5b,table_chi_len6b), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`IPhOD quartile` <- as.factor(table$`IPhOD quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `IPhOD quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
    theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD breakdown with quartiles computed for 2-6 phonemes across all mother and child words, this time computing quartiles individually for each phonemic length

<br>

```{r freq_length4, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2b <- c(sum(freq_lengths[["mod_len2b"]]$freq_qu1), sum(freq_lengths[["mod_len2b"]]$freq_qu2),sum(freq_lengths[["mod_len2b"]]$freq_qu3),sum(freq_lengths[["mod_len2b"]]$freq_qu4))
table_chi_len2b <- table_chi_len2b/sum(table_chi_len2b)*100
table_chi_len3b <- c(sum(freq_lengths[["mod_len3b"]]$freq_qu1), sum(freq_lengths[["mod_len3b"]]$freq_qu2),sum(freq_lengths[["mod_len3b"]]$freq_qu3),sum(freq_lengths[["mod_len3b"]]$freq_qu4))
table_chi_len3b <- table_chi_len3b/sum(table_chi_len3b)*100
table_chi_len4b <- c(sum(freq_lengths[["mod_len4b"]]$freq_qu1), sum(freq_lengths[["mod_len4b"]]$freq_qu2),sum(freq_lengths[["mod_len4b"]]$freq_qu3),sum(freq_lengths[["mod_len4b"]]$freq_qu4))
table_chi_len4b <- table_chi_len4b/sum(table_chi_len4b)*100
table_chi_len5b <- c(sum(freq_lengths[["mod_len5b"]]$freq_qu1), sum(freq_lengths[["mod_len5b"]]$freq_qu2),sum(freq_lengths[["mod_len5b"]]$freq_qu3),sum(freq_lengths[["mod_len5b"]]$freq_qu4))
table_chi_len5b <- table_chi_len5b/sum(table_chi_len5b)*100
table_chi_len6b <- c(sum(freq_lengths[["mod_len6b"]]$freq_qu1), sum(freq_lengths[["mod_len6b"]]$freq_qu2),sum(freq_lengths[["mod_len6b"]]$freq_qu3),sum(freq_lengths[["mod_len6b"]]$freq_qu4))
table_chi_len6b <- table_chi_len6b/sum(table_chi_len6b)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `IPhOD quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2b,table_chi_len3b,table_chi_len4b,table_chi_len5b,table_chi_len6b), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`IPhOD quartile` <- as.factor(table$`IPhOD quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `IPhOD quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
    theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** MODEL breakdown with quartiles computed for 2-6 phonemes across all mother and child words, this time computing quartiles individually for each phonemic length

<br> 
<br> 

### Maternal Frequency
Frequency based on Mothers' corpus. Children's words that are not present in the maternal speech have no frequency value and therefore were excluded. Therefore, words' frequency always starts from 1. This could be seen in the graphs below, where the first quartile (word frequency < 1) contains 0% of words.

<br>

#### Quantiles table

```{r echo = FALSE, message=FALSE, warning=FALSE}
  mot_freq %>%
    filter(UnTrn %in% (mot_uni_on_mot_freq$phon %>% 
                         unlist() %>%
                         c(chi_uni_on_mot_freq$phon %>% 
                             unlist())
    )) %>%
    .$SFreq %>%
    quantile(na.rm = TRUE) %>%
  as.matrix() %>%
  t() %>%
  kable()
```

<br>

```{r freq_mot_main, echo = FALSE, results='asis', fig.width=16, fig.height=9}
plot_freq <- function(df, main_title) {
  ggplot(df, aes(x=section, y=freq_qu1_perc, fill=baby, shape="Q1")) + 
  geom_point(size=4, alpha=0.2) +
  scale_x_continuous(breaks=c(1, seq(5,20, 5))) +
  labs(x = " ", y = " ") +
  ggtitle(main_title) +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) +
  geom_point(aes(x=section, y=freq_qu2_perc, fill=baby, shape="Q2"),size=4, alpha=0.2) + 
  geom_point(aes(x=section, y=freq_qu3_perc, fill=baby, shape="Q3"), size=4,alpha=0.2) + 
  geom_point(aes(x=section, y=freq_qu4_perc, fill=baby, shape="Q4"), size=4,alpha=0.2) + 
  scale_shape_manual("Mot Quartile", values=c(`Q1`= 0, `Q2`= 3, `Q3` = 2, `Q4`=1),
                     breaks=c("Q4","Q3", "Q2","Q1"))+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  guides(fill=FALSE)+
  geom_smooth(aes(x=section, y=freq_qu1_perc,linetype="Q1"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=freq_qu2_perc,linetype="Q2"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=freq_qu3_perc,linetype="Q3"), fill=NA, colour="black", method="lm", size=0.8)+
  geom_smooth(aes(x=section, y=freq_qu4_perc,linetype="Q4"), fill=NA, colour="black", method="lm", size=0.8)+
  theme(axis.text=element_text(size=18),         legend.text = element_text(size = 20),         legend.title = element_text(size = 20),         legend.key.size = unit(1, "cm"))+     scale_colour_grey(start = 0, end = .9)+
  scale_linetype_manual("Mot Quartile", values=c(`Q4` = "dotdash", `Q1` = "longdash",`Q2` = "solid", `Q3`= "dotted"), breaks=c("Q4","Q3", "Q2","Q1"))
}

plot1 <- plot_freq(chi_uni_on_mot_freq, "Children") 
plot2 <- plot_freq(mod_on_mot_freq, "Model") 
plot3 <- plot_freq(mot_uni_on_mot_freq, "Mothers") 

grid_arrange_shared_legend(plot3, plot1, plot2, position = "right", 
                           x_title = "Stage", y_title = "Novel words (%)",
                           x_size = 25, y_size = 25,
                           widths1 = 2, widths2 = 0.5, hjust1 = 1)
```

**Figure.** Breakdown of Maternal frequency by quartile

<br>

### Maternal Frequency at each phonemic word length

<br>

```{r freq_mot_length1, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(freq_mot_lengths[["chi_uni_len2"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len2"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len2"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len2"]]$freq_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(freq_mot_lengths[["chi_uni_len3"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len3"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len3"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len3"]]$freq_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(freq_mot_lengths[["chi_uni_len4"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len4"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len4"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len4"]]$freq_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len5 <- c(sum(freq_mot_lengths[["chi_uni_len5"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len5"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len5"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len5"]]$freq_qu4))
table_chi_len5 <- table_chi_len5/sum(table_chi_len5)*100
table_chi_len6 <- c(sum(freq_mot_lengths[["chi_uni_len6"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len6"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len6"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len6"]]$freq_qu4))
table_chi_len6 <- table_chi_len6/sum(table_chi_len6)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `Mot quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2,table_chi_len3,table_chi_len4,table_chi_len5,table_chi_len6), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`Mot quartile` <- as.factor(table$`Mot quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `Mot quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD breakdown with quartiles computed for 2-6 phonemes across all mother and child words, using the same quartiles to breakdown each length

<br>

```{r freq_mot_length2, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(freq_mot_lengths[["mod_len2"]]$freq_qu1), sum(freq_mot_lengths[["mod_len2"]]$freq_qu2),sum(freq_mot_lengths[["mod_len2"]]$freq_qu3),sum(freq_mot_lengths[["mod_len2"]]$freq_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(freq_mot_lengths[["mod_len3"]]$freq_qu1), sum(freq_mot_lengths[["mod_len3"]]$freq_qu2),sum(freq_mot_lengths[["mod_len3"]]$freq_qu3),sum(freq_mot_lengths[["mod_len3"]]$freq_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(freq_mot_lengths[["mod_len4"]]$freq_qu1), sum(freq_mot_lengths[["mod_len4"]]$freq_qu2),sum(freq_mot_lengths[["mod_len4"]]$freq_qu3),sum(freq_mot_lengths[["mod_len4"]]$freq_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len5 <- c(sum(freq_mot_lengths[["mod_len5"]]$freq_qu1), sum(freq_mot_lengths[["mod_len5"]]$freq_qu2),sum(freq_mot_lengths[["mod_len5"]]$freq_qu3),sum(freq_mot_lengths[["mod_len5"]]$freq_qu4))
table_chi_len5 <- table_chi_len5/sum(table_chi_len5)*100
table_chi_len6 <- c(sum(freq_mot_lengths[["mod_len6"]]$freq_qu1), sum(freq_mot_lengths[["mod_len6"]]$freq_qu2),sum(freq_mot_lengths[["mod_len6"]]$freq_qu3),sum(freq_mot_lengths[["mod_len6"]]$freq_qu4))
table_chi_len6 <- table_chi_len6/sum(table_chi_len6)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `Mot quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2,table_chi_len3,table_chi_len4,table_chi_len5,table_chi_len6), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`Mot quartile` <- as.factor(table$`Mot quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `Mot quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** MODEL breakdown with quartiles computed for 2-6 phonemes across all mother and child words, using the same quartiles to breakdown each length

<br>

```{r freq_mot_length3, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2b <- c(sum(freq_mot_lengths[["chi_uni_len2b"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len2b"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len2b"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len2b"]]$freq_qu4))
table_chi_len2b <- table_chi_len2b/sum(table_chi_len2b)*100

table_chi_len3b <- c(sum(freq_mot_lengths[["chi_uni_len3b"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len3b"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len3b"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len3b"]]$freq_qu4))
table_chi_len3b <- table_chi_len3b/sum(table_chi_len3b)*100
table_chi_len4b <- c(sum(freq_mot_lengths[["chi_uni_len4b"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len4b"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len4b"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len4b"]]$freq_qu4))
table_chi_len4b <- table_chi_len4b/sum(table_chi_len4b)*100
table_chi_len5b <- c(sum(freq_mot_lengths[["chi_uni_len5b"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len5b"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len5b"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len5b"]]$freq_qu4))
table_chi_len5b <- table_chi_len5b/sum(table_chi_len5b)*100
table_chi_len6b <- c(sum(freq_mot_lengths[["chi_uni_len6b"]]$freq_qu1), sum(freq_mot_lengths[["chi_uni_len6b"]]$freq_qu2),sum(freq_mot_lengths[["chi_uni_len6b"]]$freq_qu3),sum(freq_mot_lengths[["chi_uni_len6b"]]$freq_qu4))
table_chi_len6b <- table_chi_len6b/sum(table_chi_len6b)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `Mot quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2b,table_chi_len3b,table_chi_len4b,table_chi_len5b,table_chi_len6b), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`Mot quartile` <- as.factor(table$`Mot quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `Mot quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
    theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD breakdown with quartiles computed for 2-6 phonemes across all mother and child words, this time computing quartiles individually for each phonemic length

<br>

```{r freq_mot_length4, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2b <- c(sum(freq_mot_lengths[["mod_len2b"]]$freq_qu1), sum(freq_mot_lengths[["mod_len2b"]]$freq_qu2),sum(freq_mot_lengths[["mod_len2b"]]$freq_qu3),sum(freq_mot_lengths[["mod_len2b"]]$freq_qu4))
table_chi_len2b <- table_chi_len2b/sum(table_chi_len2b)*100
table_chi_len3b <- c(sum(freq_mot_lengths[["mod_len3b"]]$freq_qu1), sum(freq_mot_lengths[["mod_len3b"]]$freq_qu2),sum(freq_mot_lengths[["mod_len3b"]]$freq_qu3),sum(freq_mot_lengths[["mod_len3b"]]$freq_qu4))
table_chi_len3b <- table_chi_len3b/sum(table_chi_len3b)*100
table_chi_len4b <- c(sum(freq_mot_lengths[["mod_len4b"]]$freq_qu1), sum(freq_mot_lengths[["mod_len4b"]]$freq_qu2),sum(freq_mot_lengths[["mod_len4b"]]$freq_qu3),sum(freq_mot_lengths[["mod_len4b"]]$freq_qu4))
table_chi_len4b <- table_chi_len4b/sum(table_chi_len4b)*100
table_chi_len5b <- c(sum(freq_mot_lengths[["mod_len5b"]]$freq_qu1), sum(freq_mot_lengths[["mod_len5b"]]$freq_qu2),sum(freq_mot_lengths[["mod_len5b"]]$freq_qu3),sum(freq_mot_lengths[["mod_len5b"]]$freq_qu4))
table_chi_len5b <- table_chi_len5b/sum(table_chi_len5b)*100
table_chi_len6b <- c(sum(freq_mot_lengths[["mod_len6b"]]$freq_qu1), sum(freq_mot_lengths[["mod_len6b"]]$freq_qu2),sum(freq_mot_lengths[["mod_len6b"]]$freq_qu3),sum(freq_mot_lengths[["mod_len6b"]]$freq_qu4))
table_chi_len6b <- table_chi_len6b/sum(table_chi_len6b)*100
table <- data.frame(`Phonemic length` = c(rep(2,4),rep(3,4),rep(4,4),rep(5,4),rep(6,4)),
                    `Mot quartile` = rep(c("Q1","Q2","Q3","Q4"),5),
                    `Novel words (%)`= c(table_chi_len2b,table_chi_len3b,table_chi_len4b,table_chi_len5b,table_chi_len6b), check.names = F)
table$`Phonemic length` <- as.factor(table$`Phonemic length`)
table$`Mot quartile` <- as.factor(table$`Mot quartile`)
ggplot(table, aes(`Phonemic length`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `Mot quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
    theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** MODEL breakdown with quartiles computed for 2-6 phonemes across all mother and child words, this time computing quartiles individually for each phonemic length

<br> 

### Neighbourhood Density at each general frequency quartile

<br>

```{r nei_freq_1, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(nei_freqs[["chi_nei_freq2"]]$nei_qu1), sum(nei_freqs[["chi_nei_freq2"]]$nei_qu2),sum(nei_freqs[["chi_nei_freq2"]]$nei_qu3),sum(nei_freqs[["chi_nei_freq2"]]$nei_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(nei_freqs[["chi_nei_freq3"]]$nei_qu1), sum(nei_freqs[["chi_nei_freq3"]]$nei_qu2),sum(nei_freqs[["chi_nei_freq3"]]$nei_qu3),sum(nei_freqs[["chi_nei_freq3"]]$nei_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(nei_freqs[["chi_nei_freq4"]]$nei_qu1), sum(nei_freqs[["chi_nei_freq4"]]$nei_qu2),sum(nei_freqs[["chi_nei_freq4"]]$nei_qu3),sum(nei_freqs[["chi_nei_freq4"]]$nei_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(nei_freqs[["chi_nei_freq1"]]$nei_qu1), sum(nei_freqs[["chi_nei_freq1"]]$nei_qu2),sum(nei_freqs[["chi_nei_freq1"]]$nei_qu3),sum(nei_freqs[["chi_nei_freq1"]]$nei_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`General Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `ND quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`General Frequency` <- as.factor(table$`General Frequency`)
table$`ND quartile` <- as.factor(table$`ND quartile`)
ggplot(table, aes(`General Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `ND quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD Percentage of words in each ND quartile across general frequency quartiles

<br>

```{r nei_freq_2, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(nei_freqs[["mod_nei_freq2"]]$nei_qu1), sum(nei_freqs[["mod_nei_freq2"]]$nei_qu2),sum(nei_freqs[["mod_nei_freq2"]]$nei_qu3),sum(nei_freqs[["mod_nei_freq2"]]$nei_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(nei_freqs[["mod_nei_freq3"]]$nei_qu1), sum(nei_freqs[["mod_nei_freq3"]]$nei_qu2),sum(nei_freqs[["mod_nei_freq3"]]$nei_qu3),sum(nei_freqs[["mod_nei_freq3"]]$nei_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(nei_freqs[["mod_nei_freq4"]]$nei_qu1), sum(nei_freqs[["mod_nei_freq4"]]$nei_qu2),sum(nei_freqs[["mod_nei_freq4"]]$nei_qu3),sum(nei_freqs[["mod_nei_freq4"]]$nei_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(nei_freqs[["mod_nei_freq1"]]$nei_qu1), sum(nei_freqs[["mod_nei_freq1"]]$nei_qu2),sum(nei_freqs[["mod_nei_freq1"]]$nei_qu3),sum(nei_freqs[["mod_nei_freq1"]]$nei_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`General Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `ND quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`General Frequency` <- as.factor(table$`General Frequency`)
table$`ND quartile` <- as.factor(table$`ND quartile`)
ggplot(table, aes(`General Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `ND quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** Model Percentage of words in each ND quartile across general frequency quartiles

<br> 

### Neighbourhood Density at each maternal frequency quartile

<br>

```{r nei_mot_freq_1, echo = FALSE, results='asis', fig.width=14, fig.height=6, warning=FALSE, message=FALSE}
table_chi_len2 <- c(sum(nei_mot_freqs[["chi_nei_freq2"]]$nei_qu1), sum(nei_mot_freqs[["chi_nei_freq2"]]$nei_qu2),sum(nei_mot_freqs[["chi_nei_freq2"]]$nei_qu3),sum(nei_mot_freqs[["chi_nei_freq2"]]$nei_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(nei_mot_freqs[["chi_nei_freq3"]]$nei_qu1), sum(nei_mot_freqs[["chi_nei_freq3"]]$nei_qu2),sum(nei_mot_freqs[["chi_nei_freq3"]]$nei_qu3),sum(nei_mot_freqs[["chi_nei_freq3"]]$nei_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(nei_mot_freqs[["chi_nei_freq4"]]$nei_qu1), sum(nei_mot_freqs[["chi_nei_freq4"]]$nei_qu2),sum(nei_mot_freqs[["chi_nei_freq4"]]$nei_qu3),sum(nei_mot_freqs[["chi_nei_freq4"]]$nei_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(nei_mot_freqs[["chi_nei_freq1"]]$nei_qu1), sum(nei_mot_freqs[["chi_nei_freq1"]]$nei_qu2),sum(nei_mot_freqs[["chi_nei_freq1"]]$nei_qu3),sum(nei_mot_freqs[["chi_nei_freq1"]]$nei_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`Maternal Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `ND quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`Maternal Frequency` <- as.factor(table$`Maternal Frequency`)
table$`ND quartile` <- as.factor(table$`ND quartile`)
ggplot(table, aes(`Maternal Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `ND quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD Percentage of words in each ND quartile across Maternal Frequency quartiles

<br>

```{r nei_mot_freq_2, echo = FALSE, results='asis', fig.width=14, fig.height=6, warning=FALSE, message=FALSE}
table_chi_len2 <- c(sum(nei_mot_freqs[["mod_nei_freq2"]]$nei_qu1), sum(nei_mot_freqs[["mod_nei_freq2"]]$nei_qu2),sum(nei_mot_freqs[["mod_nei_freq2"]]$nei_qu3),sum(nei_mot_freqs[["mod_nei_freq2"]]$nei_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(nei_mot_freqs[["mod_nei_freq3"]]$nei_qu1), sum(nei_mot_freqs[["mod_nei_freq3"]]$nei_qu2),sum(nei_mot_freqs[["mod_nei_freq3"]]$nei_qu3),sum(nei_mot_freqs[["mod_nei_freq3"]]$nei_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(nei_mot_freqs[["mod_nei_freq4"]]$nei_qu1), sum(nei_mot_freqs[["mod_nei_freq4"]]$nei_qu2),sum(nei_mot_freqs[["mod_nei_freq4"]]$nei_qu3),sum(nei_mot_freqs[["mod_nei_freq4"]]$nei_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(nei_mot_freqs[["mod_nei_freq1"]]$nei_qu1), sum(nei_mot_freqs[["mod_nei_freq1"]]$nei_qu2),sum(nei_mot_freqs[["mod_nei_freq1"]]$nei_qu3),sum(nei_mot_freqs[["mod_nei_freq1"]]$nei_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`Maternal Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `ND quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`Maternal Frequency` <- as.factor(table$`Maternal Frequency`)
table$`ND quartile` <- as.factor(table$`ND quartile`)
ggplot(table, aes(`Maternal Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `ND quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** Model Percentage of words in each ND quartile across Maternal Frequency quartiles

<br> 

### Phonotactic probability at each general frequency quartile

<br>

```{r pp_freq_1, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(pp_freqs[["chi_pp_freq2"]]$ph_pr_qu1), sum(pp_freqs[["chi_pp_freq2"]]$ph_pr_qu2),sum(pp_freqs[["chi_pp_freq2"]]$ph_pr_qu3),sum(pp_freqs[["chi_pp_freq2"]]$ph_pr_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(pp_freqs[["chi_pp_freq3"]]$ph_pr_qu1), sum(pp_freqs[["chi_pp_freq3"]]$ph_pr_qu2),sum(pp_freqs[["chi_pp_freq3"]]$ph_pr_qu3),sum(pp_freqs[["chi_pp_freq3"]]$ph_pr_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(pp_freqs[["chi_pp_freq4"]]$ph_pr_qu1), sum(pp_freqs[["chi_pp_freq4"]]$ph_pr_qu2),sum(pp_freqs[["chi_pp_freq4"]]$ph_pr_qu3),sum(pp_freqs[["chi_pp_freq4"]]$ph_pr_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(pp_freqs[["chi_pp_freq1"]]$ph_pr_qu1), sum(pp_freqs[["chi_pp_freq1"]]$ph_pr_qu2),sum(pp_freqs[["chi_pp_freq1"]]$ph_pr_qu3),sum(pp_freqs[["chi_pp_freq1"]]$ph_pr_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`General Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`General Frequency` <- as.factor(table$`General Frequency`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`General Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD Percentage of words in each LOG PP quartile across general frequency quartiles

<br>

```{r pp_freq_2, echo = FALSE, results='asis', fig.width=14, fig.height=6}
table_chi_len2 <- c(sum(pp_freqs[["mod_pp_freq2"]]$ph_pr_qu1), sum(pp_freqs[["mod_pp_freq2"]]$ph_pr_qu2),sum(pp_freqs[["mod_pp_freq2"]]$ph_pr_qu3),sum(pp_freqs[["mod_pp_freq2"]]$ph_pr_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(pp_freqs[["mod_pp_freq3"]]$ph_pr_qu1), sum(pp_freqs[["mod_pp_freq3"]]$ph_pr_qu2),sum(pp_freqs[["mod_pp_freq3"]]$ph_pr_qu3),sum(pp_freqs[["mod_pp_freq3"]]$ph_pr_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(pp_freqs[["mod_pp_freq4"]]$ph_pr_qu1), sum(pp_freqs[["mod_pp_freq4"]]$ph_pr_qu2),sum(pp_freqs[["mod_pp_freq4"]]$ph_pr_qu3),sum(pp_freqs[["mod_pp_freq4"]]$ph_pr_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(pp_freqs[["mod_pp_freq1"]]$ph_pr_qu1), sum(pp_freqs[["mod_pp_freq1"]]$ph_pr_qu2),sum(pp_freqs[["mod_pp_freq1"]]$ph_pr_qu3),sum(pp_freqs[["mod_pp_freq1"]]$ph_pr_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`General Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`General Frequency` <- as.factor(table$`General Frequency`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`General Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** Model Percentage of words in each LOG PP quartile across general frequency quartiles

<br> 

### Phonotactic probability at each maternal frequency quartile

<br>

```{r pp_mot_freq_1, echo = FALSE, results='asis', fig.width=14, fig.height=6, warning=FALSE, message=FALSE}
table_chi_len2 <- c(sum(pp_mot_freqs[["chi_pp_freq2"]]$ph_pr_qu1), sum(pp_mot_freqs[["chi_pp_freq2"]]$ph_pr_qu2),sum(pp_mot_freqs[["chi_pp_freq2"]]$ph_pr_qu3),sum(pp_mot_freqs[["chi_pp_freq2"]]$ph_pr_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(pp_mot_freqs[["chi_pp_freq3"]]$ph_pr_qu1), sum(pp_mot_freqs[["chi_pp_freq3"]]$ph_pr_qu2),sum(pp_mot_freqs[["chi_pp_freq3"]]$ph_pr_qu3),sum(pp_mot_freqs[["chi_pp_freq3"]]$ph_pr_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(pp_mot_freqs[["chi_pp_freq4"]]$ph_pr_qu1), sum(pp_mot_freqs[["chi_pp_freq4"]]$ph_pr_qu2),sum(pp_mot_freqs[["chi_pp_freq4"]]$ph_pr_qu3),sum(pp_mot_freqs[["chi_pp_freq4"]]$ph_pr_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(pp_mot_freqs[["chi_pp_freq1"]]$ph_pr_qu1), sum(pp_mot_freqs[["chi_pp_freq1"]]$ph_pr_qu2),sum(pp_mot_freqs[["chi_pp_freq1"]]$ph_pr_qu3),sum(pp_mot_freqs[["chi_pp_freq1"]]$ph_pr_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`Maternal Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`Maternal Frequency` <- as.factor(table$`Maternal Frequency`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`Maternal Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Children") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** CHILD Percentage of words in each LOG PP quartile across Maternal Frequency quartiles

<br>

```{r pp_mot_freq_2, echo = FALSE, results='asis', fig.width=14, fig.height=6, warning=FALSE, message=FALSE}
table_chi_len2 <- c(sum(pp_mot_freqs[["mod_pp_freq2"]]$ph_pr_qu1), sum(pp_mot_freqs[["mod_pp_freq2"]]$ph_pr_qu2),sum(pp_mot_freqs[["mod_pp_freq2"]]$ph_pr_qu3),sum(pp_mot_freqs[["mod_pp_freq2"]]$ph_pr_qu4))
table_chi_len2 <- table_chi_len2/sum(table_chi_len2)*100
table_chi_len3 <- c(sum(pp_mot_freqs[["mod_pp_freq3"]]$ph_pr_qu1), sum(pp_mot_freqs[["mod_pp_freq3"]]$ph_pr_qu2),sum(pp_mot_freqs[["mod_pp_freq3"]]$ph_pr_qu3),sum(pp_mot_freqs[["mod_pp_freq3"]]$ph_pr_qu4))
table_chi_len3 <- table_chi_len3/sum(table_chi_len3)*100
table_chi_len4 <- c(sum(pp_mot_freqs[["mod_pp_freq4"]]$ph_pr_qu1), sum(pp_mot_freqs[["mod_pp_freq4"]]$ph_pr_qu2),sum(pp_mot_freqs[["mod_pp_freq4"]]$ph_pr_qu3),sum(pp_mot_freqs[["mod_pp_freq4"]]$ph_pr_qu4))
table_chi_len4 <- table_chi_len4/sum(table_chi_len4)*100
table_chi_len1 <- c(sum(pp_mot_freqs[["mod_pp_freq1"]]$ph_pr_qu1), sum(pp_mot_freqs[["mod_pp_freq1"]]$ph_pr_qu2),sum(pp_mot_freqs[["mod_pp_freq1"]]$ph_pr_qu3),sum(pp_mot_freqs[["mod_pp_freq1"]]$ph_pr_qu4))
table_chi_len1 <- table_chi_len1/sum(table_chi_len1)*100

table <- data.frame(`Maternal Frequency` = c(rep(1,4),rep(2,4),rep(3,4),rep(4,4)),
                    `PP quartile` = rep(c("Q1","Q2","Q3","Q4"),4),
                    `Novel words (%)`= c(table_chi_len1,table_chi_len2,table_chi_len3,table_chi_len4), check.names = F)
table$`Maternal Frequency` <- as.factor(table$`Maternal Frequency`)
table$`PP quartile` <- as.factor(table$`PP quartile`)
ggplot(table, aes(`Maternal Frequency`, `Novel words (%)`)) + 
  geom_bar(aes(fill = `PP quartile`), stat = "identity", position = "dodge")+
  scale_y_continuous(limits=c(0, 100), breaks=seq(0, 100, by = 10))+
  scale_fill_grey()+
  theme(axis.text=element_text(size=20),
        axis.title=element_text(size=20),
        legend.text = element_text(size=20),
        legend.title = element_text(size = 20),
        legend.key.size = unit(1,"cm"))+
  ggtitle("Model") +
  theme(plot.title = element_text(hjust = 0.5, size = 25)) 
```

**Figure .** Model Percentage of words in each LOG PP quartile across Maternal Frequency quartiles
